Appendix 1: sdmTMB statistical model description

### 2022-05-06 doc/appendix-model.Rmd
Double space; update appendices for latest sdmTMB
SVC not limited to 1 now

---
title: "Appendix 1: sdmTMB statistical model description"
output:
  bookdown::pdf_document2:
    highlight: pygments
    toc: true
    number_sections: true
fig_caption: true
urlcolor: blue
highlight: "monochrome"
csl: mee.csl
bibliography: refs.bib
header-includes:
  \usepackage[left]{lineno}
  \usepackage{bm}
  \usepackage{amssymb}
---

@@

where $\boldsymbol{\zeta}$ is a random field representing a spatially varying coefficient.
Usually, $\bm{X}^{\mathrm{svc}}_{\s, t}$ would represent a prediction matrix that is constant spatially for a given time $t$.
Currently, $\bm{X}^{\mathrm{svc}}_{t}$ is restricted to a single covariate (column vector), supplied by a one-sided formula to `spatial_varying`.
For example `spatial_varying = ~ 0 + x`, where `0` omits the intercept.

>>>>

---
title: "Appendix 1: sdmTMB statistical model description"
output:
  bookdown::pdf_document2:
    highlight: pygments
    toc: true
    number_sections: true
fig_caption: true
urlcolor: blue
highlight: "monochrome"
csl: mee.csl
bibliography: refs.bib
header-includes:
  \usepackage[left]{lineno}
  \usepackage{bm}
  \usepackage{amssymb}
  \linenumbers
---

@@

where $\boldsymbol{\zeta}$ is a random field representing a spatially varying coefficient.
Usually, $\bm{X}^{\mathrm{svc}}_{\s, t}$ would represent a prediction matrix that is constant spatially for a given time $t$ as defined by a one-sided formula supplied to `spatial_varying`.
For example `spatial_varying = ~ 0 + x`, where `0` omits the intercept.
